New first figure

### 2021-05-12 manuscript/bef_stability/appendixB.Rmd
Reviewed according to willem comments

The monitoring of the fish communities occurs in streams varying in size, shape
and depth. Stream characteristics constrain the type of protocol
applied. Small streams (depth < 0.7m across the entire width) are sampled with
the "complete" protocol. Anodes are distributed across the width of the river
then one to three electric fidhing events are performed. We selected only the
data from the first event to homogenize the sampling effort. In deeper and wider
streams (depth >= 0.7m), the sampling is
partial over the bank and the channel and it is performed by boat and by foot
(along the bank). We selected only the sampling done over the bank because the
channel was not systematically sampled. Two types of partial protocols takes
place: "partial over bank" and "partial by points", which are respectively
continuous and discrete samplings. We considered both types of partial protocols
in our analysis. In the "partial by point" protocol, the channel was sometimes
sampled as well, so we selected only the "partial by point" sampling in which
all the sampling points were done over the bank to homogenize the sampling. Some
sampled stations were located in streams with intermediate characteristics where
both "complete" and "partial" protocols were alternatively used depending on the
state of the stream at the time of sampling. For these sites, we only kept the
samples that had been carried out with the most frequently used protocol.

Heterogeneity in the sampling date may introduce variability due to different
climatic or environmental conditions but also to the life cycle of the species.
For instance, early surveys may precede the egg hatching and youngs-of-the-year.
In order to reduce heterogeneity in the sampling date, only one sampling per
year was retained if there were more in a given year, the one that had the most
species and then the most individuals. Finally, most of the fish sampling
occurred in September (Median: mid-August). There was low heterogeneity of the
sampling month within stations, with the median sampling month being mid-August
where the median standard deviation of the sampling month was  month, i.e. three
weeks. To further reduce sampling heterogeneity, we only kept the sampling in
which the length of stream sampled along the stream was inside the median length
sampled more or less 30%.

@@

The procedures to obtain altitude, slope, width and depth of the streams are fully
explained in main text. Because those measurements were collected during the
fishing protocol, they were easier to manage in the analyses. Then, we detail
in the following sections how water temperature, water flow and Biological
Oxygen Demand (BOD) variables were obtained. In the following section, we will
present how we averaged each variable to match the annual fish monitoring
events. We also detailed how we interpolated these variables to match the
spatial location of the fish samplings.

@@

The interpolations were carried out by hydrographic basin due to convergence
issues when the interpolation was carried out at the scale of the whole
France. We had to find a trade-off between the number of data (to keep 
high enough to perform the interpolation) and the level of dataset splitting. We then
merged some hydrographic basins to end up with four regions of interpolation:
West, East, South and North.

@@

When predicted values were below the minimum value or above the maximum value
recorded in the dataset for flow, temperature and BOD, we replaced the
predicted value by respectively the minimum and the maximum value found in the
dataset. We ran the interpolation four times, and we kept the predicted value
which had the smaller standard deviation.

@@

The CV of biomass over time can cover multiple temporal dynamics, including
increases, stable, decreases and a mix of them. Theoretically, however, the CV
computed to quantify stability is often represented with the assumption that the
overall dynamic of the biomass varies around an equilibrium
[@kefi_advancing_2019]. In order to approach the condition of equilibrium, we
kept only the stations that show no clear temporal trends. To characterise the
biomass temporal dynamics according to their trajectories, we used the symbolic
aggregated approximation method (SAX), which is commonly used in time series
analysis and implemented in the `jmotif` R package [@senin_grammarviz_2018].
This method classifies time series rather than quantifies trends. Therefore, it
is enough generic to encompass a diversity of temporal trajectories. The
classification necessitates three steps. The time series are first normalized.
Then, we reduced the dimensionality of the time series by a Piecewise
Aggregation Approximation (PAA) method. Each time series is divided into $N$
frames of equal size that allows to reduce the dimensionality of the time
series. For each frame, we simply kept the mean value of the time series.  The
final stage is to qualify each frame into string. Because values of normalized
time series typically follows a normal distribution ($N(0,1)$), a breakpoint can
be computed by dividing the area under the normal distribution in equal parts.
The algorithm attributes an alphabetic letter to each part from the lowest to
the highest ($a$, $b$, $c$, ...). We set three breakpoints, so $a$, $b$ and $c$.
Finally, the trajectory of each time series is classified as a combination of
$a$, $b$, $c$ letters. $abc$ and $cba$ time series represent respectively
monotonic increasing and decreasing trajectories. For data analysis, we kept
only the $bbb$ which represent time series that showed no temporal tendencies,
with respect to our methodology.

@@

```{r, cache = FALSE}
caption_mod_res <- paste0(
  "Residuals versus fitted values of the linear models included in the structural
  equation models."
) 
```

@@

```{r, fig.height = 7, fig.cap = sens_cap}
p_sens_bm <- plot_sensivity_analysis(
  .data = sem_bm_results,
  inverse_label_order = TRUE) +
  labs(x = "", title = "Median of annual community biomass") +
  theme(legend.position = "none", plot.margin = unit(c(0, 0, 0, 28), units = "mm"))

p_sens_stab <- plot_sensivity_analysis(.data = sem_stab_results,
  inverse_label_order = TRUE) +
  labs(title = "Temporal stability of annual community biomass") +
  guides(color = guide_legend(direction = "horizontal", nrow = 2))
legend_b <- get_legend(p_sens_stab)
p_sens_stab %<>% + theme(legend.position = "none", plot.margin = unit(c(0,0,0,27), units = "mm"))
p <- plot_grid(
  p_sens_bm, p_sens_stab, legend_b, nrow = 3,
  rel_heights = c(1, 1, .1)
  #,
  #labels = c("Total biomass", "Biomass stability")
)
p
```

>>>>

The monitoring of the fish communities occurs in streams varying in size, shape
and depth. Stream characteristics constrain the type of protocol
applied. Small streams (depth < 0.7m across the entire width) are sampled with
the "complete" protocol. Anodes are distributed across the width of the river
then one to three electric fishing events are performed. We selected only the
data from the first event to homogenize the sampling effort. In deeper and wider
streams (depth >= 0.7m), this protocol is partial and is carried out along the
banks and the channel and it is performed by boat and by foot (along the bank).
We selected only the sampling done over the bank because the
channel was not systematically sampled. Two types of partial protocols take
place: "partial over bank" and "partial by points", which are respectively
a continuous and discrete fishing events. We considered both types of partial protocols
in our analysis. In the "partial by point" protocol, the channel was sometimes
sampled as well, so we selected only the "partial by point" sampling in which
all the sampling points were done over the bank to homogenize the sampling. Some
sampled stations were located in streams with intermediate characteristics where
both "complete" and "partial" protocols were alternatively used depending on the
state of the stream at the time of sampling. For these sites, we only kept the
samples that had been carried out with the most frequently used protocol.

Heterogeneity in the fishing date may introduce variability due to different
climatic or environmental conditions but also to the life cycle of the species.
For instance, early surveys may precede the egg hatching and youngs-of-the-year.
In order to reduce heterogeneity in the sampling date, only one sampling per
year was retained if there were more in a given year, the one that had the most
species and then the most individuals. Finally, most of the fish sampling
occurred in September (Median: mid-August). There was low heterogeneity of the
sampling month within stations, with the median sampling month being mid-August
where the median standard deviation of the sampling month was  month, i.e. three
weeks. To further reduce sampling heterogeneity, we only kept the sampling in
which the length of stream sampled along the stream was inside the median length
sampled more or less 30%.

@@

The procedures to obtain altitude, slope, width and depth of the streams are fully
explained in main text. Because those measurements were collected during the
fishing protocol, they were easier to manage in the analyses. Then, we detail
in the following sections how water temperature, water flow and Biological
Oxygen Demand (BOD) variables were obtained. In the following section, we 
present how we averaged each variable to match the annual fish monitoring
events. We also detail how we interpolated these variables to match the
spatial location of the fish samplings.

@@

The interpolations were carried out by hydrographic basin due to convergence
issues when the interpolation was carried out at the scale of the whole
country. We had to find a trade-off between the number of data (to keep 
high enough to perform the interpolation) and the level of dataset splitting. We then
merged some hydrographic basins to end up with four regions of interpolation:
West, East, South and North.

@@

When predicted values were below the minimum value or above the maximum value
recorded in the dataset for flow, temperature and BOD, we replaced the
predicted value by respectively the minimum and the maximum value found in the
dataset. We ran the interpolation four times, and we kept the predicted value
which had the smallest standard deviation.

@@

The CV of biomass over time can cover multiple temporal dynamics, including
increases, decreases, no trends or and a mixture of the above. Theoretically, however, the CV
computed to quantify stability is often represented with the assumption that the
overall dynamic of the biomass varies around an equilibrium
[@kefi_advancing_2019]. In order to approach the condition of equilibrium, we
kept only the stations that show no clear temporal trends. To characterise the
biomass temporal dynamics according to their trajectories, we used the symbolic
aggregated approximation method (SAX), which is commonly used in time series
analysis and implemented in the `jmotif` R package [@senin_grammarviz_2018].
This method classifies time series rather than quantifies trends. Therefore, it
is generic enough to encompass a diversity of temporal trajectories. The
classification necessitates three steps. The time series are first normalized.
Then, the dimensionality of the time series is reduced by a Piecewise
Aggregation Approximation (PAA) method. Each time series is divided into $N$
frames of equal size that allows to reduce the dimensionality of the time
series. For each frame, we simply kept the mean value of the time series.  The
final stage is to qualify each frame into string. Because values of normalized
time series typically follow a normal distribution ($N(0,1)$), a breakpoint can
be computed by dividing the area under the normal distribution in equal parts.
The algorithm attributes an alphabetic letter to each part from the lowest to
the highest ($a$, $b$, $c$, ...). We set three breakpoints, so $a$, $b$ and $c$.
Finally, the trajectory of each time series is classified as a combination of
$a$, $b$, $c$ letters. $abc$ and $cba$ time series represent respectively
monotonic increasing and decreasing trajectories. For data analysis, we kept
only the $bbb$ which represent time series that showed no temporal tendencies,
with respect to our methodology.

@@

```{r, cache = FALSE}
caption_mod_res <- paste0(
  "Residuals versus fitted values from the linear models included in the structural
  equation models."
) 
```

@@

```{r, fig.height = 7.5, fig.cap = sens_cap}
p_sens_bm <- plot_sensivity_analysis(
  .data = sem_bm_results,
  inverse_label_order = TRUE) +
  labs(x = "", title = "Median of annual community biomass") +
  theme(legend.position = "none", plot.margin = unit(c(0, 0, 0, 28), units = "mm"))

p_sens_stab <- plot_sensivity_analysis(.data = sem_stab_results,
  inverse_label_order = TRUE) +
  labs(title = "Temporal stability of annual community biomass") +
  guides(color = guide_legend(direction = "horizontal", nrow = 2))
legend_b <- get_legend(p_sens_stab)
p_sens_stab %<>% + theme(legend.position = "none", plot.margin = unit(c(0,0,0,27), units = "mm"))
p <- plot_grid(
  p_sens_bm, p_sens_stab, legend_b, nrow = 3,
  rel_heights = c(1, 1, .12)
  #,
  #labels = c("Total biomass", "Biomass stability")
)
p
```

### 2021-05-12 manuscript/bef_stability/fig1_biomass_network.Rmd
Reviewed according to willem comments

```{r}
myload(metaweb_analysis,  dir = mypath("data"))
sp_color <- set_color_species(
  node_list = colnames(metaweb_analysis$metaweb),
  resource_list = metaweb_analysis$resource
)
node_sp <- str_extract(colnames(metaweb_analysis$metaweb), "[A-Z|a-z]*")
sp_color[node_sp]
names(sp_color)[names(sp_color) %in% meta$resource] <- 
  c("detritivore", "biofilm", "phytobenthos", "macrophage", "phytoplankton", "zooplankton", "zoobenthos")

>>>>

```{r}
myload(metaweb_analysis,  dir = mypath("data"))
sp_color <- set_color_species(
  node_list = colnames(metaweb_analysis$metaweb),
  resource_list = metaweb_analysis$resource
)
node_sp <- str_extract(colnames(metaweb_analysis$metaweb), "[A-Z|a-z]*")
sp_color[node_sp]
names(sp_color)[names(sp_color) %in% metaweb_analysis$resource] <- 
  c("detritivore", "biofilm", "phytobenthos", "macrophage", "phytoplankton", "zooplankton", "zoobenthos")
